A Large-scale Study of Polymorphism in R

### 2019-03-26 paper/main.tex
minor

In this section, we present our dataset. R is designed to accommodate data
analysts.  Typical workflows go from data import, to data cleaning, followed
by steps of modeling, transformation and visualization. Often, the code that
implements these analysis pipelines together with their results resides in
notebooks. Unfortunately notebooks are typically not shared in public
repositories such as GitHub, and if they were, the data required to run them
would surely not be shared. For this reason our analysis focuses on
packages; these bundle reusable units of R code with documentation, sample
data, use-cases and tests.

>>>>

In this section, we present our dataset. R aims to accommodate data
analysts, their workflows start with data import, followed by cleaning, and
then by steps of modeling, transformation and visualization. Often, the code
of these analysis pipelines resides, together with the data and results, in
notebooks. Few notebooks are publicly shared, and when they are, the data
isn't. For this reason our
analysis focuses on packages; these bundle reusable units of R code with
documentation, sample data and use-cases.
